### 2010-06-23 paper/IIWAS2010/content/introduction.tex
Added QA related work section

In addition, Morpheus assumes term categories are come from a
\textit{consistent} realm-based ontology. By consistency we mean it has two
properties: (i) singly-rooted heterarchy (acyclic digraph wiyh unique 
ancestor of all nodes) (ii) the subclass/superclass relations have meaningful 
semantic interpretations. This is important because, our proposed similarity 
measure for categories is based on the heterarchically
structured category ontologies. Moreover, when a regular user enters a query,
Morpheus ranks SSQs in the store based on this catgeory similarity. Suppose a
regular user asks -\textit{ a 1997 Toyota Camry V6 needs what size tires?} In
this query, identifying \textit{Camry V6} as a subclass of \textit{Toyota} cars
and a predecessor of \textit{automobile models} is important, because this will
help us grouping stored queries. Similarly, a clean ontology-taxonomy can
improve the recall of such queries by supporting transitivity and other types of
inference like faceted browsing \cite{Wu2008}.

>>>>

In addition, Morpheus assumes term categories are come from a
\textit{consistent} realm-based ontology. By consistency we mean it has two
properties: (i) singly-rooted heterarchy (acyclic digraph with unique 
ancestor of all nodes) (ii) the subclass/superclass relations have meaningful 
semantic interpretations. This is important because, our proposed similarity 
measure for categories is based on the heterarchically
structured category ontologies. Moreover, when a regular user enters a query,
Morpheus ranks SSQs in the store based on this catgeory similarity. Suppose a
regular user asks -\textit{ a 1997 Toyota Camry V6 needs what size tires?} In
this query, identifying \textit{Camry V6} as a subclass of \textit{Toyota} cars
and a predecessor of \textit{automobile models} is important, because this will
help us grouping stored queries. Similarly, a clean ontology-taxonomy can
improve the recall of such queries by supporting transitivity and other types of
inference like faceted browsing \cite{Wu2008}.

### 2010-06-23 paper/IIWAS2010/content/related_work.tex
Added QA related work section

>>>>

Question Answering (QA) is an old field and there has been a recent influx of QA work. The earliest question answering systems include BASEBALL \cite{Green1961} and Lunar \cite{woods1973} were both \emph{closed domain} and \emph{closed corpus}.  Closed domain QA systems are those in which the possible meanings of the questions given are finite. We define closed corpus sytems as those in which the sources used to answer questions are finite.  QA systems that treat the web as a document collection is considered an open corpus system.  The morpheus system is considered an open corpus system.  It goes beyond current state of the art QA systems by examining deep web sources.

Several community QA systems have been developed, one of the most popular being Yahoo! Answers \cite{yahooanswers2008}.  These sites enlist a community of users to answer question posed by other users.  This idea has evolved to invent socially integrated QA systems have emerged such as Aardvark \cite{vark2010}. In addition to having questions answered by users, aardvark is able to contact potential answers through several mediums beyond its webpage (e.g. instant message, mobile phone).  This allows for a possibly faster answers to questions.  The morpheus system relies on both user interface and the property of similar question being answered by a community of users to give a fast reliable answer.
